Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
Diego : context,study design

>>>>

\subsubsection{Context, Study Design}
It was the first time we where trying a long-terme interaction between a child
and the CoWriter robot. So the first aim of this study was to see if such an
interaction was simply possible. If we could create an environement to keep a child engaged
during one hour just in writing words with the robot.
The second question was focused on the content of the interaction. Our goal was
to figure out what extent the child would actually improve the robot's
writing.\\

Diego is a 5 years hold child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplifiyed by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

The experiment took one month. It was divided in four sessions of one hour, one session per week.
In order to justify to the child an activity where a robot wants to learn
handwriting, we decided to adduce a scenario. There where two Nao robots: a
blue one (Mimi) and an orange one (Clem). They where introduced to the child as
two hold friends. Mimi was left, and the two robots were corresponding by
handwrited mails. But Clem was begining in writing and it needed the help of
Diego to write its responses to Mimi.\\

During the first session, Diego was just teaching single letters to the robot.
progressively we increased the difficulty : the second session he was teaching
shirt words and in third session he was teaching long sentences. The last session was more like a test for Clem
: it had to prove to Mimi that it actually improved its handwriting thanks to
Diego.
